---
title: "RNA-Seq analysis report."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

Data from user(showed 10 first rows):
``` {r echo=FALSE, results='asis'}
library(knitr)
kable(userBase()[1:10,])
```

Box plot of expression levels via samples:
``` {r echo=FALSE}
expr_via_samples()
```

Density plot of expression levels via samples:
``` {r echo=FALSE}
density_via_samples()
```

Table of top DE (differentially expressed) genes:
``` {r echo=FALSE, results='asis'}
library(knitr)
kable(smallp_table())
```

Box plot of specific genes (top 10):
``` {r echo=FALSE}
de_genes_expr()
```

Heat map of z-scaled levels of gene expression:
``` {r echo=FALSE}
heatmap_reactiv()
```

Volcano plot of gene expression (satisfying requirements genes are blue):
``` {r echo=FALSE}
volcano_plot()
```

Table with downloaded annotations from Biomart:
``` {r echo=FALSE,results='asis'}
library(knitr)
if (!is.null(do_raportu$BM)) {
  return(kable(do_raportu$BM))
}else{
  return(NULL)}
```
